\section{Innovation}
Pioneering work has motivated a novel perspective that epilepsy is a disease of neuronal circuitry through which spreading pathologic activity disrupts neural function (i.e. rhythmic motor activity, altered cognition, or abnormal sensation) \cite{kutsy1999ictal, spencer2002neural}. Since, investigators have focused on the spatial distributions of epileptic activity using multiscale neural signals in ECoG and sub-millimeter $\mu$ECoG to more accurately localize where seizures start and how their pathologic activity affects distributed cortical structures \cite{worrell2008high-frequency, schevon2009spatial, stead2010microseizures, viventi2011flexible, feldt_muldoon2013spatially, weiss2013ictal}. More formally, investigators seek the functional organization of a complex epileptic network \cite{spencer2002neural, kramer2012epilepsy, lehnertz2014evolving}.
~\\
~\\
\bflin{Aim 1:} \textbf{Identify topological abnormalities in the epileptic network as seizures begin and evolve.}
For this aim I will \textbf{innovate} novel methods to study how network topology reorganizes over time and relate specific functional connections to network dynamics. Prior fMRI studies have explored gross whole-brain network reorganization during task states \cite{bassett2006adaptive, bassett2011dynamic}, however these approaches have neither been adapted to study meso-scale network structure nor been used to relate network phenomena to neurophysiologic events. The developed algorithms will need to assess network geometry to separate seizure-generating from surrounding epileptogenic network components and track functional connections \cite{holme2012temporal} within and between each set of components.
~\\
~\\
\bflin{Aim 2:} \textbf{Localize seizure generating network and differentiate from surrounding epileptogenic network through inter-ictal topological abnormalities.}
Functional communication pathways of a network can be interpreted as indicators of network regions that co-activate under some particular set of brain dynamics within a window of time. Because these functional relationships arise due to hard-wired structural connectivity, through either gray or white matter, abnormalities in the epileptic network are believed to be discernible not just during seizures but also inter-ictally. For this aim I will \textbf{innovate} network decomposition algorithms that can relate network topology between seizures and the inter-ictal periods that precede them. These decomposition approaches will need to dissociate healthy inter-ictal sub-network topologies from their pathologic counterparts.
~\\
~\\
\bflin{Aim 3:} \textbf{Evaluate localization accuracy and specificity of the seizure generating network in patients.}
A variety of factors affect the efficacy by which clinicians delineate and impact the epileptic network. From an anatomical perspective the presence of a lesion on brain imaging immediately improves the chances of seizure freedom through surgical resection \cite{french2007refractory}. From a functional perspective seizures may either remain focal or secondarily spread, and implicate a much larger area of the epileptogenic network, affecting the target size for therapy. There is a lacking quantitative description to discriminate actual therapeutic targets from normal functioning cortex. An automated network-based approach for mapping the epileptic network provides this description alongside a novel and \textbf{innovative} way to compare network neurophysiology within and between clinical cohorts of different etiology.

