% SPECIFIC AIMS -- PLACEHOLDER
\setlist{nolistsep}
Medically refractory epilepsy has traditionally been diagnosed and treated by localizing and surgically resecting cortical tissue comprising seizure "foci." Recent work explains poor seizure freedom post-surgery (~40\% in patients with nonlesional epilepsy) by re-defining epilepsy as a network disease with pathologic connectivity between cortical structures. These insights have spawned new implantable neuromodulation devices to control brain regions that generate seizures without removing them. In this research proposal I will address the following three questions critical for mapping epileptic networks and localizing connections to target with neuromodulation:
\begin{enumerate}[topsep=1ex, itemsep=0pt]
    \item How are dynamic functional connections in epileptic networks topologically organized?
    \item To what extent can the epileptic network be mapped intraoperatively?
    \item How do structural connections facilitate functional communication in epileptic networks?
\end{enumerate}

%%% AIM 1
\hangindent=6ex
\noindent
\bflin{Aim 1:} \textbf{Characterize dynamic functional interactions in naturally-occurring epileptic networks.}

\hangindent=6ex
\textbf{Hypothesis:} Functional connections within the epileptic network reconfigure during epileptiform activity.

\hangindent=6ex
\textbf{Challenge:} To determine dynamic functional connectivity from intracranial recordings and classify and track this connectivity in order to understand time-dependent topological properties of epileptic networks.

\hangindent=6ex
\textbf{Approach:} I will develop connectivity metrics to compare signals from intracranial neural sensors. I will also design algorithms to relate network configurations over time, augmenting existing dynamic network analysis methods.

\hangindent=6ex
\textbf{Impact:} These algorithms will help quantify the spatial involvement of distributed cortical structures during epileptiform events. Relating geometric space of sensors to epileptic network topology will also help determine which circuits to target with implantable neuromodulation devices.


%%% AIM 2
\hangindent=\parindent
\hangafter=1
\noindent
\bflin{Aim 2:} \textbf{Determine how intraoperative functional connectivity relates to extraoperative functional connectivity during epileptiform events.}

\hangindent=6ex
\textbf{Hypothesis:} Functional connectivity based on intraoperative intracranial recordings can help map the epileptic network.

\hangindent=6ex
\textbf{Challenge:} To investigate effects of anesthesia on functional connectivity and retrospectively characterize connections in intraoperative functional networks involved in epileptiform events.

\hangindent=6ex
\textbf{Approach:} I will collect high-bandwidth intracranial recordings in the operating room under anesthesia types known to enhance epileptiform activity. I will adapt approaches developed in \bflin{Aim 1} to characterize functional connectivity in intraoperative epileptic networks and compare to extraoperative network configurations.

\hangindent=6ex
\textbf{Impact:} These methods will yield relationships between connections present under extraoperative and intraoperative conditions. They can also inform online network classification methods to immediately map the epileptic network intraoperatively.


%%% AIM 3
\hangindent=\parindent
\hangafter=1
\noindent
\bflin{Aim 3:} \textbf{Localize structural white-matter architecture underlying functional communication in epileptic networks.}

\hangindent=6ex
\textbf{Hypothesis:} Structural connectivity is predictive of spatial spread of pathologic epileptiform activity.

\hangindent=6ex
\textbf{Challenge:} To establish white-matter fiber connectivity between regions of interest within the epileptic network and determine which tracts propagate epileptic activity.

\hangindent=6ex
\textbf{Approach:} I will engineer imaging techniques to reconstruct and track fiber pathways that stem from intracranial sensor locations. I will then expand statistical algorithms developed in \bflin{Aim 1} to constrain functional relationships based on structural connections.

\hangindent=6ex
\textbf{Impact:} These methods will help trace white-matter fiber pathways that are complicit in functional dynamics of epileptic events. They will help innovate new clinical interventions that prevent epileptiform activity from propagating to cortical structures critical to eloquent function.
